### 2021-04-26 input/introduction.tex
intro reworkd with bullet and contribution

\begin{asparadesc} %% to remove left-margin :p
\item [$\bullet$] We highlight the properties that guarantee
  decentralized consistent partitioning in dynamic infrastructures. We
  demonstrate that concurrent creation and removal of partitions may
  impair the propagation of control information crucial for consistent
  partitioning. Yet, \processes are able to purge stale information
  forever using only neighbor-to-neighbor communication, hence leaving
  room for up-to-date information propagation, and eventually
  consistent partitioning.
\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions in the system. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.
\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
  empirically support our complexity analysis and the scalability of
  \NAME in large scale networks comprising 10k \processes. Our
  experiments also highlight the relevance of \NAME in autonomous
  systems. \NAME would allow to lock down the traffic generated by
  content indexing, even in contexts where \emph{physical}
  partitioning may occur.
\end{asparadesc}

@@

\noindent \NAME can constitute a new building block for
geo-distributed services.

>>>>

\begin{asparadesc} %% to remove left-margin :p
\item [$\bullet$] We highlight the properties that guarantee
  decentralized consistent partitioning in dynamic infrastructures. We
  demonstrate that concurrent creation and removal of partitions may
  impair the propagation of control information crucial for consistent
  partitioning. Yet, \processes are able to purge stale information
  forever using only neighbor-to-neighbor communication, hence leaving
  room for up-to-date information propagation, and eventually
  consistent partitioning.

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes join, leave, and crash at any time. \NAME's efficiency
  relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.

\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
  empirically support our complexity analysis and the scalability of
  \NAME. Using scoped broadcast, \NAME quickly disseminate messages to
  a subset of relevant \processes. The higher the number of
  partitions, the smaller \NAME's overhead.  Most importantly, \NAME
  does not generate traffic in quiescent systems.  Our experiments
  also highlight the relevance of \NAME in autonomous systems. \NAME
  would allow to lock down the traffic generated by content indexing,
  even in contexts where \emph{physical} partitioning may occur.
  As such, \NAME can constitute a new building block for geo-distributed
  services.
\end{asparadesc}

@@
